---
title: "Predictor Distributions including HIV"
output: predictor_distributions_hiv
---
```{r}
setwd("C://Users/mario/OneDrive/Desktop/backupaxel/ClassIandII/withHIV/results/")
# Basic plotting libraries
library(ggplot2)
library(cowplot)
# Statistical analyses libraries
library(magrittr)
library(dplyr)
library(overlapping)
```

#################################
Supp Figure 1: 
Distributions of Epitope & non-
epitope residues by predictor

```{r}
virus_distributions <- read.csv("PredictionValueDistributions.txt", header = T, sep = " ",stringsAsFactors=FALSE)
virus_distributions$Classifier <- as.factor(virus_distributions$Classifier)
virus_distributions$Classifier <- factor(virus_distributions$Classifier, labels = c("Non-Epitope","Epitope"))
```

----comparison of mean REU
```{r}
mu <- virus_distributions %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(ResE))

resE.ttest <- t.test(data=virus_distributions, ResE ~ Classifier)
resE.p <- resE.ttest$p.value

virus.distributions.ResE <- ggplot(virus_distributions,aes(x=ResE, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="Per-residue REU",y="Density") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + xlim(-10,10) + theme_cowplot() + theme(legend.position = "bottom", legend.justification = "center", legend.direction = "horizontal", legend.box = "vertical") + guides(color=guide_legend(nrow=1,byrow=TRUE, title.position = "top", title.hjust = 0.6))

classifier_legend <- get_legend(virus.distributions.ResE)

virus.distributions.ResE <- ggplot(virus_distributions,aes(x=ResE, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="Per-residue REU",y="Density") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + xlim(-10,10) + theme_cowplot() + theme(legend.position = "none") 
virus.distributions.ResE
```
```{r}
resE.p
```
----comparison of mean contact proximity RMSD
```{r}
mu <- virus_distributions %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(CP))
CP.ttest <- t.test(data=virus_distributions, CP ~ Classifier)
CP.p <- CP.ttest$p.value
virus.distributions.CP <- ggplot(virus_distributions,aes(x=CP, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="CP RMSD",y="Density") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + xlim(0,2) + theme_cowplot() + theme(legend.position = "none") 
virus.distributions.CP
```
```{r}
CP.p
```
----comparison of mean neighbor vector
```{r}
mu <- virus_distributions %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NV))
NV.ttest <- t.test(data=virus_distributions, NV ~ Classifier)
NV.p <- NV.ttest$p.value
virus.distributions.NV <- ggplot(virus_distributions,aes(x=NV, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NV",y="Density") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + xlim(0,1) + theme_cowplot() + theme(legend.position = "none")
virus.distributions.NV
```
```{r}
NV.p
```
```{r}
SFig1 <- plot_grid(virus.distributions.NV, virus.distributions.ResE, virus.distributions.CP, nrow = 1, labels = "auto")
SFig1 <- plot_grid(SFig1, classifier_legend, ncol = 1, rel_heights = c(1,0.2))
SFig1
```
----------------overlap of predictors
-----Neighbor Vector
```{r}
epitope.values <- subset(virus_distributions, Classifier == "Epitope")
nonepitope.values <- subset(virus_distributions, Classifier == "Non-Epitope")
NV.distributions <- list(X1=epitope.values$NV, X2=nonepitope.values$NV)
NV.overlap <- overlap(NV.distributions, n = length(epitope.values$NV))
NV.overlap$OV
```
-----per residue REU
```{r}
ResE.distributions <- list(X1=epitope.values$ResE, X2=nonepitope.values$ResE)
ResE.overlap <- overlap(ResE.distributions, n = length(epitope.values$ResE))
ResE.overlap$OV
```

-----Contact Proximity RMSD
```{r}
CP.distributions <- list(X1=epitope.values$CP, X2=nonepitope.values$CP)
CP.overlap <- overlap(CP.distributions, n = length(epitope.values$CP))
CP.overlap$OV
```

#################################
Supp Figure 2:
Comparison on Neighbor Sum 
distributions using radii/upper
boundary of increasing size

```{r}
ov_final <- read.csv("OV_w_leaveouts.txt", header = T, sep = " ")
ov_final$Classifier <- as.factor(ov_final$Classifier)
ov_final$Classifier <- factor(ov_final$Classifier, labels = c("Non-Epitope","Epitope"))
Bayes <- subset(ov_final, Method=="Bayes")
noREU <- subset(ov_final, Method=="noREU")
noCP <- subset(ov_final, Method=="noCP")
noNV <- subset(ov_final, Method=="noNV")
REU <- subset(ov_final, Method=="REU")
CP <- subset(ov_final, Method=="CP")
NV <- subset(ov_final, Method=="NV")
Environ <- subset(ov_final, Method=="Environ")
```
```{r}
epitope.values <- subset(Bayes, Classifier == "Epitope")
nonepitope.values <- subset(Bayes, Classifier == "Non-Epitope")
Bayes.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes.overlap <- overlap(Bayes.distributions, n = length(epitope.values$Prediction))
Bayes.overlap$OV
```
```{r}
epitope.values <- subset(noREU, Classifier == "Epitope")
nonepitope.values <- subset(noREU, Classifier == "Non-Epitope")
noREU.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
noREU.overlap <- overlap(noREU.distributions, n = length(epitope.values$Prediction))
noREU.overlap$OV
```

```{r}
epitope.values <- subset(noCP, Classifier == "Epitope")
nonepitope.values <- subset(noCP, Classifier == "Non-Epitope")
noCP.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
noCP.overlap <- overlap(noCP.distributions, n = length(epitope.values$Prediction))
noCP.overlap$OV
```
```{r}
epitope.values <- subset(noNV, Classifier == "Epitope")
nonepitope.values <- subset(noNV, Classifier == "Non-Epitope")
noNV.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
noNV.overlap <- overlap(noNV.distributions, n = length(epitope.values$Prediction))
noNV.overlap$OV
```
```{r}
epitope.values <- subset(REU, Classifier == "Epitope")
nonepitope.values <- subset(REU, Classifier == "Non-Epitope")
REU.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
REU.overlap <- overlap(REU.distributions, n = length(epitope.values$Prediction))
REU.overlap$OV
```

```{r}
epitope.values <- subset(CP, Classifier == "Epitope")
nonepitope.values <- subset(CP, Classifier == "Non-Epitope")
CP.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
CP.overlap <- overlap(CP.distributions, n = length(epitope.values$Prediction))
CP.overlap$OV
```
```{r}
epitope.values <- subset(NV, Classifier == "Epitope")
nonepitope.values <- subset(NV, Classifier == "Non-Epitope")
NV.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
NV.overlap <- overlap(NV.distributions, n = length(epitope.values$Prediction))
NV.overlap$OV
```
```{r}
epitope.values <- subset(Environ, Classifier == "Epitope")
nonepitope.values <- subset(Environ, Classifier == "Non-Epitope")
Environ.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Environ.overlap <- overlap(Environ.distributions, n = length(epitope.values$Prediction))
Environ.overlap$OV
```

Must isolate each Radius size to calculate mean 
and coefficient of overlap by group
```{r}
NS8 <- subset(virus_distributions, Radius=="8")
NS16 <- subset(virus_distributions, Radius=="16")
NS24 <- subset(virus_distributions, Radius=="24")
NS32 <- subset(virus_distributions, Radius=="32")
NS40 <- subset(virus_distributions, Radius=="40")
NS48 <- subset(virus_distributions, Radius=="48")
NS56 <- subset(virus_distributions, Radius=="56")
NS64 <- subset(virus_distributions, Radius=="64")
```

-----NS radius 8
```{r}
mu <- NS8 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS8.ttest <- t.test(data=NS8, NS ~ Classifier)
NS8.p <- NS8.ttest$p.value
NS8plot <- ggplot(NS8,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "8 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5)) + guides(title.position="center")
NS8plot
```
```{r}
NS8.p
```
```{r}
epitope.values <- subset(NS8, Classifier == "Epitope")
nonepitope.values <- subset(NS8, Classifier == "Non-Epitope")
NS8.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS8.overlap <- overlap(NS8.distributions, n = length(epitope.values$NS))
NS8.overlap$OV
```

-----NS radius 16
```{r}
mu <- NS16 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS16.ttest <- t.test(data=NS16, NS ~ Classifier)
NS16.p <- NS16.ttest$p.value
NS16plot <- ggplot(NS16,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "16 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
NS16plot
```
```{r}
NS16.p
```
```{r}
epitope.values <- subset(NS16, Classifier == "Epitope")
nonepitope.values <- subset(NS16, Classifier == "Non-Epitope")
NS16.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS16.overlap <- overlap(NS16.distributions, n = length(epitope.values$NS))
NS16.overlap$OV
```
-----NS radius 24
```{r}
mu <- NS24 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS24.ttest <- t.test(data=NS24, NS ~ Classifier)
NS24.p <- NS24.ttest$p.value
NS24plot <- ggplot(NS24,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "24 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
NS24plot
```
```{r}
NS24.p
```
```{r}
epitope.values <- subset(NS24, Classifier == "Epitope")
nonepitope.values <- subset(NS24, Classifier == "Non-Epitope")
NS24.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS24.overlap <- overlap(NS24.distributions, n = length(epitope.values$NS))
NS24.overlap$OV
```
-----NS radius32
```{r}
mu <- NS32 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS32.ttest <- t.test(data=NS32, NS ~ Classifier)
NS32.p <- NS32.ttest$p.value
NS32plot <- ggplot(NS32,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "32 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
NS32plot
```
```{r}
NS32.p
```
```{r}
epitope.values <- subset(NS32, Classifier == "Epitope")
nonepitope.values <- subset(NS32, Classifier == "Non-Epitope")
NS32.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS32.overlap <- overlap(NS32.distributions, n = length(epitope.values$NS))
NS32.overlap$OV
```
-----NS radius 40
```{r}
mu <- NS40 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS40.ttest <- t.test(data=NS40, NS ~ Classifier)
NS40.p <- NS40.ttest$p.value
NS40plot <- ggplot(NS40,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "40 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
NS40plot
```
```{r}
NS40.p
```
```{r}
epitope.values <- subset(NS40, Classifier == "Epitope")
nonepitope.values <- subset(NS40, Classifier == "Non-Epitope")
NS40.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS40.overlap <- overlap(NS40.distributions, n = length(epitope.values$NS))
NS40.overlap$OV
```
-----NS radius 48
```{r}
mu <- NS48 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS48.ttest <- t.test(data=NS48, NS ~ Classifier)
NS48.p <- NS48.ttest$p.value
NS48plot <- ggplot(NS48,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "48 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
NS48plot
```
```{r}
NS48.p
```
```{r}
epitope.values <- subset(NS48, Classifier == "Epitope")
nonepitope.values <- subset(NS48, Classifier == "Non-Epitope")
NS48.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS48.overlap <- overlap(NS48.distributions, n = length(epitope.values$NS))
NS48.overlap$OV
```
-----NS radius 56
```{r}
mu <- NS56 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS56.ttest <- t.test(data=NS56, NS ~ Classifier)
NS56.p <- NS56.ttest$p.value
NS56plot <- ggplot(NS56,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "56 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
NS56plot
```
```{r}
epitope.values <- subset(NS56, Classifier == "Epitope")
nonepitope.values <- subset(NS56, Classifier == "Non-Epitope")
NS56.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS56.overlap <- overlap(NS56.distributions, n = length(epitope.values$NS))
NS56.overlap$OV
```
-----NS radius 64
```{r}
mu <- NS64 %>%
  group_by(Classifier) %>%
  summarise(grp.mean = mean(NS))
NS64.ttest <- t.test(data=NS56, NS ~ Classifier)
NS64.p <- NS64.ttest$p.value
NS64plot <- ggplot(NS64,aes(x=NS, color=Classifier)) + geom_density(aes(y=..scaled..)) + labs(x="NS",y="Density", title = "64 Å radius") + scale_color_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + geom_vline(aes(xintercept = grp.mean, color=Classifier), data = mu, linetype = 2) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
NS64plot
```
```{r}
epitope.values <- subset(NS64, Classifier == "Epitope")
nonepitope.values <- subset(NS64, Classifier == "Non-Epitope")
NS64.distributions <- list(X1=epitope.values$NS, X2=nonepitope.values$NS)
NS64.overlap <- overlap(NS64.distributions, n = length(epitope.values$NS))
NS64.overlap$OV
```
```{r}
SFig2 <- plot_grid(NS8plot,NS16plot,NS24plot,NS32plot,NS40plot,NS48plot,NS56plot,NS64plot, nrow = 2)
SFig2 <- plot_grid(SFig2, classifier_legend, ncol = 1, rel_heights = c(1,0.2))
SFig2
```



########################################
Figure 1:
Comparison to Discotope and Ellipro

------Coefficient of overlap for predictions
```{r}
prediction_ov <- read.csv("OverlapPredictions.txt", header=T, sep = " ")
NS8ov <- subset(prediction_ov, Approach=="8")
NS16ov <- subset(prediction_ov, Approach=="16")
NS24ov <- subset(prediction_ov, Approach=="24")
NS32ov <- subset(prediction_ov, Approach=="32")
NS40ov <- subset(prediction_ov, Approach=="40")
NS48ov <- subset(prediction_ov, Approach=="48")
Bayes8ov <- subset(prediction_ov, Approach=="Bayes8")
Bayes16ov <- subset(prediction_ov, Approach=="Bayes16")
Bayes24ov <- subset(prediction_ov, Approach=="Bayes24")
Bayes32ov <- subset(prediction_ov, Approach=="Bayes32")
Bayes40ov <- subset(prediction_ov, Approach=="Bayes40")
Bayes48ov <- subset(prediction_ov, Approach=="Bayes48")
Bayes56ov <- subset(prediction_ov, Approach=="Bayes56")
Bayes64ov <- subset(prediction_ov, Approach=="Bayes64")
Elliproov <- subset(prediction_ov, Approach=="Ellipro")
Discotopeov <- subset(prediction_ov, Approach=="Discotope")
```

```{r}
epitope.values <- subset(NS8ov, Classifier == "1")
nonepitope.values <- subset(NS8ov, Classifier == "0")
NS8ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
NS8ov.overlap <- overlap(NS8ov.distributions, n = length(epitope.values$Prediction))
NS8ov.overlap$OV
```

```{r}
epitope.values <- subset(NS16ov, Classifier == "1")
nonepitope.values <- subset(NS16ov, Classifier == "0")
NS16ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
NS16ov.overlap <- overlap(NS16ov.distributions, n = length(epitope.values$Prediction))
NS16ov.overlap$OV
```
```{r}
epitope.values <- subset(NS24ov, Classifier == "1")
nonepitope.values <- subset(NS24ov, Classifier == "0")
NS24ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
NS24ov.overlap <- overlap(NS24ov.distributions, n = length(epitope.values$Prediction))
NS24ov.overlap$OV
```

```{r}
epitope.values <- subset(NS32ov, Classifier == "1")
nonepitope.values <- subset(NS32ov, Classifier == "0")
NS32ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
NS32ov.overlap <- overlap(NS32ov.distributions, n = length(epitope.values$Prediction))
NS32ov.overlap$OV
```
```{r}
epitope.values <- subset(NS40ov, Classifier == "1")
nonepitope.values <- subset(NS40ov, Classifier == "0")
NS40ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
NS40ov.overlap <- overlap(NS40ov.distributions, n = length(epitope.values$Prediction))
NS40ov.overlap$OV
```
```{r}
epitope.values <- subset(NS48ov, Classifier == "1")
nonepitope.values <- subset(NS48ov, Classifier == "0")
NS48ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
NS48ov.overlap <- overlap(NS48ov.distributions, n = length(epitope.values$Prediction))
NS48ov.overlap$OV
```
```{r}
epitope.values <- subset(Elliproov, Classifier == "1")
nonepitope.values <- subset(Elliproov, Classifier == "0")
Elliproov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Elliproov.overlap <- overlap(Elliproov.distributions, n = length(epitope.values$Prediction))
Elliproov.overlap$OV
```
```{r}
epitope.values <- subset(Discotopeov, Classifier == "1")
nonepitope.values <- subset(Discotopeov, Classifier == "0")
Discotopeov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Discotopeov.overlap <- overlap(Discotopeov.distributions, n = length(epitope.values$Prediction))
Discotopeov.overlap$OV
```


```{r}
epitope.values <- subset(Bayes8ov, Classifier == "1")
nonepitope.values <- subset(Bayes8ov, Classifier == "0")
Bayes8ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes8ov.overlap <- overlap(Bayes8ov.distributions, n = length(epitope.values$Prediction))
Bayes8ov.overlap$OV
```
```{r}
epitope.values <- subset(Bayes16ov, Classifier == "1")
nonepitope.values <- subset(Bayes16ov, Classifier == "0")
Bayes16ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes16ov.overlap <- overlap(Bayes16ov.distributions, n = length(epitope.values$Prediction))
Bayes16ov.overlap$OV
```
```{r}
epitope.values <- subset(Bayes24ov, Classifier == "1")
nonepitope.values <- subset(Bayes24ov, Classifier == "0")
Bayes24ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes24ov.overlap <- overlap(Bayes24ov.distributions, n = length(epitope.values$Prediction))
Bayes24ov.overlap$OV
```
```{r}
epitope.values <- subset(Bayes32ov, Classifier == "1")
nonepitope.values <- subset(Bayes32ov, Classifier == "0")
Bayes32ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes32ov.overlap <- overlap(Bayes32ov.distributions, n = length(epitope.values$Prediction))
Bayes32ov.overlap$OV
```
```{r}
epitope.values <- subset(Bayes40ov, Classifier == "1")
nonepitope.values <- subset(Bayes40ov, Classifier == "0")
Bayes40ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes40ov.overlap <- overlap(Bayes40ov.distributions, n = length(epitope.values$Prediction))
Bayes40ov.overlap$OV
```
```{r}
epitope.values <- subset(Bayes48ov, Classifier == "1")
nonepitope.values <- subset(Bayes48ov, Classifier == "0")
Bayes48ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes48ov.overlap <- overlap(Bayes48ov.distributions, n = length(epitope.values$Prediction))
Bayes48ov.overlap$OV
```
```{r}
epitope.values <- subset(Bayes56ov, Classifier == "1")
nonepitope.values <- subset(Bayes56ov, Classifier == "0")
Bayes56ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes56ov.overlap <- overlap(Bayes56ov.distributions, n = length(epitope.values$Prediction))
Bayes56ov.overlap$OV
```
```{r}
epitope.values <- subset(Bayes64ov, Classifier == "1")
nonepitope.values <- subset(Bayes64ov, Classifier == "0")
Bayes64ov.distributions <- list(X1=epitope.values$Prediction, X2=nonepitope.values$Prediction)
Bayes64ov.overlap <- overlap(Bayes64ov.distributions, n = length(epitope.values$Prediction))
Bayes64ov.overlap$OV
```
--------Average ROC curves by method
```{r}
ROCcomparisons <- read.csv("cumulative_ROC2.txt", header = T, sep = " ")
ROCcomparisons$Boundary <- factor(ROCcomparisons$Boundary, levels=c("Discotope","Ellipro","8","16","24","32","40","48","56","64"), labels=c("Discotope","Ellipro","Envir 8Å","Envir 16Å", "Envir 24Å","Envir 32Å","Envir 40Å","Envir 48Å","Envir 56Å","Envir 64Å"))
ROCcomparisons$Method <- factor(ROCcomparisons$Method, levels = c("Discotope","Ellipro","Envir"))

avgROC <- ggplot(ROCcomparisons, aes(fpr, tpr, color=Boundary)) + geom_line() + labs(y="Sensitivity", x="1 - Specificity") + geom_segment(x=0, y=0, xend=1, yend=1, color="black", linetype="dotted", size=1) +scale_color_manual(name="Method", values = c("#648FFF","#FE6100","gray90","gray80","gray70","gray60","gray50","gray40","gray30","gray20")) + theme_cowplot() + theme(legend.position = "bottom", legend.justification = "center", legend.text = element_text(size = 10)) + guides(color=guide_legend(title.position = "top", title.hjust = 0.5, ncol = 3))

avgROC <- ggplot(ROCcomparisons, aes(fpr, tpr, color=Boundary)) + geom_line() + labs(y="Sensitivity", x="1 - Specificity") + geom_segment(x=0, y=0, xend=1, yend=1, color="black", linetype="dotted", size=1) +scale_color_manual(name="Method", values = c("#648FFF","#FE6100","gray90","gray80","gray70","gray60","gray50","gray40","gray30","gray20")) + theme_cowplot() + theme(legend.position = "none")
avgROC
```
----------AUC values for each virus (out of sample)
```{r}
auc <- read.csv("individual_AUC.txt", header = T, sep = " ")
auc$Method <- factor(auc$Method, c("Ellipro", "Discotope", "Bayes", "Random"))
auc$Radius <- factor(auc$Radius, c("Ellipro", "Discotope", "8", "16", "24","32","40","48","56","64"))
auc$Virus <- factor(auc$Virus, labels=c("EBOV","H3 stem","H7","HIV","RSV","SARS","SARS2"))
aucplot <- ggplot(auc, aes(x=Radius, y=AUC, color=Method)) + geom_point(aes(fill=Method), size=3) + scale_color_manual(name="Method", values = c("#FE6100","#648FFF","black","gray90")) + scale_fill_manual(name="Method", values = c("#FE6100","#648FFF","black","gray90")) + ylim(0.4,1) + theme_cowplot() + facet_wrap(~ Virus, ncol = 4)+ theme(panel.border = element_rect(color="black", size = 1),strip.background = element_rect(color = "black", size = 1), axis.text.x = element_text(angle = 90, hjust = 1,size = 10), legend.position = "none", axis.title.x = element_blank()) + geom_hline(yintercept = 0.5, linetype="dashed", color="gray50") 
aucplot
```
```{r}
compareROC <- read.csv("ROC_comparison.txt", header = T, sep = " ")
compROC <- ggplot(compareROC, aes(fpr, tpr, color=Method)) + geom_line() + labs(y="Sensitivity", x="1 - Specificity") + geom_segment(x=0, y=0, xend=1, yend=1, color="black", linetype="dotted", size=1) +scale_color_manual(name="Method", values = c("black","#648FFF","#FE6100"),labels=c("AxIEM","Discotope","Ellipro")) + theme_cowplot() + theme(legend.position = "bottom", legend.justification = "center", legend.text = element_text(size = 10)) + guides(color=guide_legend(title.position = "top", title.hjust = 0.5))

compROC <- ggplot(compareROC, aes(fpr, tpr, color=Method)) + geom_line() + labs(y="Sensitivity", x="1 - Specificity") + geom_segment(x=0, y=0, xend=1, yend=1, color="black", linetype="dotted", size=1) +scale_color_manual(name="Method", values = c("black","#648FFF","#FE6100"),labels=c("AxIEM","Discotope","Ellipro")) + theme_cowplot() + theme(legend.position = "none")
compROC
```
```{r}
Fig2A <- plot_grid(aucplot,labels = c("A"))
Fig2BC <- plot_grid(avgROC, compROC, labels = c("B","C"))
Fig2 <- plot_grid(Fig2A,Fig2BC, ncol = 1, rel_heights = c(1,0.75))
Fig2
```


####################################################
Figure 3
Analysis of epitope size
```{r}
boundary.stats <- read.csv("protein_distance_comparisons.txt", header = T, sep = " ")
boundary.stats$Virus <- factor(boundary.stats$Virus, labels = c("EBOV GP","H3 HA stem","H7 HA","HIV Env","RSV F","SARS S","SARS2 S"))
```
----Comparison of Upper epitope boundary at maximum AUC value and protein residue number
```{r}
radius_model <- lm(Radius ~ Residues, data=boundary.stats)
radius_model
```

```{r}
boundary.residues <- ggplot(boundary.stats, aes(x=Residues, y=Radius)) + geom_point(aes(shape=Virus)) + geom_smooth(method = "lm",color="black") + scale_shape_manual(name="Virus", values = c(19,17,15,2,3,5,9)) + labs(x="Number of Residues",y="") + theme_cowplot() + stat_cor(label.y=60,aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) + theme(legend.title.align = 0.5, legend.justification = "center")

virus_legend <- get_legend(boundary.residues)

boundary.residues <- ggplot(boundary.stats, aes(x=Residues, y=Radius)) + geom_point(aes(shape=Virus)) + geom_smooth(method = "lm",color="black") + scale_shape_manual(name="Virus", values = c(19,17,15,2,3,5,9)) + labs(x="Number of Residues",y="") + theme_cowplot() + stat_cor(label.y=65,aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) + theme(legend.position = "none")
boundary.residues
```
```{r}
boundary.maxresolution <- ggplot(boundary.stats, aes(x=MaxResolution, y=Radius)) + geom_point(aes(shape=Virus)) + geom_smooth(method = "lm",color="black") + scale_shape_manual(name="Virus", values = c(19,17,15,2,3,5,9)) + labs(x="Highest Resolution (Å)", y="") + theme_cowplot() + stat_cor(label.y=70,aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) + theme(legend.position = "none")
boundary.maxresolution
```
```{r}
boundary.minresolution <- ggplot(boundary.stats, aes(x=MinResolution, y=Radius)) + geom_point(aes(shape=Virus)) + geom_smooth(method = "lm",color="black") + scale_shape_manual(name="Virus", values = c(19,17,15,2,3,5,9)) + labs(x="Lowest Resolution (Å)", y="") + theme_cowplot() + stat_cor(label.y=75,aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) + theme(legend.position = "none")
boundary.minresolution
```
```{r}
boundary.maxdistance <- ggplot(boundary.stats, aes(x=MaxDistance, y=Radius)) + geom_point(aes(shape=Virus)) + geom_smooth(method = "lm",color="black") + scale_shape_manual(name="Virus", values = c(19,17,15,2,3,5,9)) + labs(x="Largest Cα-Cα Distance (Å)", y="") + theme_cowplot() + stat_cor(label.y=80,aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) + theme(legend.position = "none")
boundary.maxdistance
```

```{r}
boundary.epitopes <- ggplot(boundary.stats, aes(x=FractionEpitope, y=Radius)) + geom_point(aes(shape=Virus)) + geom_smooth(method = "lm",color="black") + scale_shape_manual(name="Virus", values = c(19,17,15,2,3,5,9)) + labs(x="Epitope Fraction", y="") + theme_cowplot() + stat_cor(label.y=70,aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) + theme(legend.position = "none")
boundary.epitopes
```
```{r}
boundary.conformations <- ggplot(boundary.stats, aes(x=Conformations, y=Radius)) + geom_point(aes(shape=Virus)) + geom_smooth(method = "lm",color="black") + scale_shape_manual(name="Virus", values = c(19,17,15,2,3,5,9)) + labs(x="Epitope Fraction", y="") + theme_cowplot() + stat_cor(label.y=70,aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) + theme(legend.position = "none")
boundary.conformations
```
```{r}
SFig3 <- plot_grid(boundary.residues,boundary.maxresolution,boundary.minresolution,boundary.maxdistance,boundary.epitopes,boundary.conformations, nrow = 2)
SFig3 <- plot_grid(SFig3,virus_legend, rel_widths = c(1,0.25))
SFig3
```



###############################################
Leave outs
```{r}
leave1outs <- read.csv("leave1out_ROC.txt", header = T, sep = " ")
l1ROC <- ggplot(leave1outs, aes(fpr, tpr, color=leftout)) + geom_line() + labs(y="Sensitivity", x="1 - Specificity",title="Excluded") + geom_segment(x=0, y=0, xend=1, yend=1, color
                                                                                                                                                     ="black", linetype="dotted", size=1) +scale_color_manual(name="", values = c("black","#9933FF","pink","#FE6100"),labels=c("none","CP","NV","REU")) + theme_cowplot() + theme(legend.text = element_text(size = 10),plot.title = element_text(hjust = 0.5))
l1ROC
```
```{r}
leave2outs <- read.csv("leave2out_ROC.txt", header = T, sep = " ")
l2ROC <- ggplot(leave2outs, aes(fpr, tpr, color=leftin)) + geom_line() + labs(y="Sensitivity", x="1 - Specificity",title="Included") + geom_segment(x=0, y=0, xend=1, yend=1, color="black", linetype="dotted", size=1) +scale_color_manual(name="", values = c("black","#9933FF","pink","#FE6100"),labels=c("all","CP","NV","REU")) + theme_cowplot() + theme(legend.text = element_text(size = 10), plot.title = element_text(hjust = 0.5))
l2ROC
```
```{r}
SFig4 <- plot_grid(l1ROC, l2ROC, nrow = 1)
SFig4
```




####################################
Subfigure for Fig1
Bayes 2d distributions
```{r}
ResE.dists <- ggplot(virus_distributions,aes(x=ResE, fill=Classifier)) + geom_density(aes(y=..scaled..),alpha=0.25) + labs(x="Per-residue REU",y="Density") + scale_fill_manual(name = "Epitope Classification", values = c("grey10", "dodgerblue")) + xlim(-10,10) + theme_cowplot() + theme(legend.position = "none", axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(),axis.line = element_blank()) 
ResE.dists
```
```{r}
NS48dists <- ggplot(NS48,aes(x=NS, fill=Classifier)) + geom_density(aes(y=..scaled..),alpha=0.25) +  scale_fill_manual(name = "", values = c("grey10", "dodgerblue")) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5), axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(),axis.line = element_blank()) + coord_flip()
NS48dists
```
```{r}
dists_scatter <- ggplot(NS48, aes(x=ResE, y=NS, color=Classifier)) + geom_point(alpha=0.04) + xlim(-10,10) + scale_color_manual(name = "", values = c("grey10", "dodgerblue")) + stat_ellipse(type = "norm", size=2.5) + theme_cowplot() + theme(legend.position = "none", plot.title = element_text(hjust = 0.5), axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(),axis.line = element_blank()) 
dists_scatter
```

```{r}
blankPlot <- ggplot()+geom_blank(aes(1,1))+
  theme(plot.background = element_blank(), 
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(), 
   panel.border = element_blank(),
   panel.background = element_blank(),
   axis.title.x = element_blank(),
   axis.title.y = element_blank(),
   axis.text.x = element_blank(), 
   axis.text.y = element_blank(),
   axis.ticks = element_blank()
     )
Fig1<-grid.arrange(ResE.dists, blankPlot, dists_scatter, NS48dists, 
        ncol=2, nrow=2, widths=c(4, 1.4), heights=c(1.4, 4))
plot_grid(Fig1)
```


